IML Term project paper

### 2022-12-23 paper.rmd
Update paper.rmd

We tried the model with both the full dataset and the dataset with 36 variables, of which the model with the fewer variables performed better. We used that model as our Random Forest classifier.

@@

The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|ccc|}
\hline
Model type & Loo-CV accuracy & Loo-CV perplexity&Binary accuracy on test data & Binary accuracy on npf_test\\
\hline
Dummy model & 0 & 2.01&\\
Logistic regression & 0.8728448 & 1.338286&0.8445596\\
Naive Bayes & 0.8125 & 166.084 &\\
LDA & 0.8922414 & 1.32923 &\\
QDA & 0.8534483 & 6.34633 &\\
SVM & 0.8793103 & -&0.8435233\\
Lasso & 0.8965517 & 1.29399&0.8746114\\
Random Forest & 0.89 & 1.35\\
GBM &	0.8943966 & 1.324385 & 0.8746114 \\
\hline
\end{tabular}
\end{table}

>>>>

We tried the model with both the full dataset and the dataset with 36 variables, of which the model with all the variables performed a little better. We used that model as our Random Forest classifier.

@@

The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|ccc|}
\hline
Model type & Loo-CV accuracy & Loo-CV perplexity&Binary accuracy on test data & Binary accuracy on npf_test\\
\hline
Dummy model & 0 & 2.01&\\
Logistic regression & 0.8728448 & 1.338286&0.8445596\\
Naive Bayes & 0.8125 & 166.084 &\\
LDA & 0.8922414 & 1.32923 &\\
QDA & 0.8534483 & 6.34633 &\\
SVM & 0.8793103 & -&0.8435233\\
Lasso & 0.8965517 & 1.29399&0.8746114\\
Random Forest & 0.887931 & 1.329754 & 0.8673575\\
GBM &	0.8943966 & 1.324385 & 0.8746114 \\
\hline
\end{tabular}
\end{table}
